$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-12-09 paper/paper.tex
Bring the def of Unused into the paper

The first three rules ($\constr{comp}-$*) state associativity, symmetry, and $\PO$ as being the neutral element of parallel composition, respectively.
The last three ($\constr{scope}-$*) state garbage collection, scope extrusion and commutativity of restrictions, respectively.
In $\constr{scope-ext}$ the type $\Unused_i \; Q$ is an inductive proof asserting that the variable index $i$ does not appear neither in the inputs nor in the outputs of $Q$ (see \autoref{app:definitions}).
The function $\func{lower}_i \; Q \; uQ$ traverses $Q$ decrementing every index greater than $i$.
In $\constr{scope-comm}$ the function $\func{exchange}_i \; P$ traverses $P$ (of type $\allowbreak \Process_{\suc \suc n}$) and swaps variable references $i$ and $\suc i$.
In all the above, $i$ is incremented every time we go under a binder.

>>>>

The first three rules ($\constr{comp}-$*) state associativity, symmetry, and $\PO$ as being the neutral element of parallel composition, respectively.
The last three ($\constr{scope}-$*) state garbage collection, scope extrusion and commutativity of restrictions, respectively.
In $\constr{scope-ext}$ the type $\Unused_i \; Q$ is an inductive proof asserting that the variable index $i$ does not appear neither in the inputs nor in the outputs of $Q$ (see \autoref{def:unused}).
The function $\func{lower}_i \; Q \; uQ$ traverses $Q$ decrementing every index greater than $i$.
In $\constr{scope-comm}$ the function $\func{exchange}_i \; P$ traverses $P$ (of type $\allowbreak \Process_{\suc \suc n}$) and swaps variable references $i$ and $\suc i$.
In all the above, $i$ is incremented every time we go under a binder.

\begin{nidefinition}
  \label{def:unused}
  A variable $i$ is unused in $P$ ($\Unused_i \; P$) if it appears in none of its inputs and none of its outputs.
  \todo{should we have this as a figure instead?}

  \begin{mathpar}
    \datatype
    {i : \Var_n \\ P : \Process_n}
    {\Unused_i \; P}
    \; \textsc{Unused}

    \inferrule
    { }
    {\Unused_i \; \PO}

    \inferrule
    {\Unused_{\suc i} \; P}
    {\Unused_i \; \new{}P}

    \inferrule
    {\Unused_i \; P \\ \Unused_i \; Q}
    {\Unused_i \; \comp{P}{Q}}

    \inferrule
    {i \type{\not\equiv} x \\ \Unused_{\suc i} \; P}
    {\Unused_i \; \recv{x}{} P}

    \inferrule
    {i \type{\not\equiv} x \\ i \type{\not\equiv} y \\ \Unused_i \; P}
    {\Unused_i \; \send{x}{y} P}
  \end{mathpar}

  The type $i \type{\not\equiv} x$ unfolds to the negation of propositional equality on \textsc{Var}, i.e. $i \type{\equiv} x \to \type{\bot}$.
\end{nidefinition}
